\href{http://www.sigcomm.org/content/ebook}{Recent Advances in Networking}

### 2013-08-02 Compiled/intro/intro.tex
dd logo:
fix
added c4 figs
fixes

Professors often rely on textbooks to teach undergraduate and graduate networking courses. While there are many good introductory textbooks, there are very few books on advanced networking topics that could be suitable to graduate courses in networking. To fill this gap, SIGCOMM Education Committee has launched a community project to develop a high-quality, open-source, edited eBook on “Recent Advances in Networking”. This eBook will be distributed online via the SIGCOMM website.

@@

\begin{figure}
\begin{center}
\includegraphics[width=3cm]{intro/sigcomm-logo-new}
%\caption{\label{kmeans} {ACM SIGCOMM}}\vspace{-3mm}
\end{center}
\end{figure}
%August 2013 \\
\vspace{1in}
Hamed Haddadi, Olivier Bonaventure, ``Recent Advances in Networking", Volume 1, ACM SIGCOMM eBook, August 2013.

>>>>

Professors often rely on textbooks to teach undergraduate and graduate networking courses. While there are many good introductory textbooks, there are very few books on advanced networking topics that could be suitable to graduate courses in networking. To fill this gap, SIGCOMM Education Committee has launched a community project to develop a high-quality, open-source, edited eBook on ``Recent Advances in Networking". This eBook will be distributed online via the SIGCOMM website.

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=3cm]{intro/sigcomm-logo-new}
%%\caption{\label{kmeans} {ACM SIGCOMM}}\vspace{-3mm}
%\end{center}
%\end{figure}
%August 2013 \\
\vspace{1in}
Hamed Haddadi and Olivier Bonaventure (editors), ``Recent Advances in Networking", Volume 1, ACM SIGCOMM eBook, August 2013.
